%-------------------------
% Resume in Latex
% Author : Justin Napolitano
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://cv.jnapolitano.io/}{\Large Justin Napolitano}} & Email : \href{mailto:justin@jnapolitano,io}{justin@jnapolitano.io}\\
  \href{https://cv.jnapolitano.io}{https:cv.jnapolitano.io} & Mobile : +1-832-299-0372 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Central Florida}{Orlando, Fl}
      {Bachelor of Arts in Political Science}{August 2018}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://cv.jnapolitano.io/parts/data/web-scraping/index.html}{BTJN, LLC}}{Houston, TX}
      {Software Developer}{May 2021 - Present}
      \resumeItemListStart
        \resumeItem{\href{https://cv.jnapolitano.io/parts/data/web-scraping/index.html}{Sales Lead Generation Application}}
          {\href{https://cv.jnapolitano.io/parts/data/web-scraping/index.html}{Produced 10,000 sales leads weekly on average for a marketing firm.  Mined web for data with Python and Bs4.} \href{https://cv.jnapolitano.io/parts/python-development/google/index.html}{Integrated data with custom Google API class.}  Identified valuable leads with \href{https://cv.jnapolitano.io/parts/python-development/neo4j/index.html}{Neo4j} and \href{https://cv.jnapolitano.io/parts/python-development/janus-graph/index.html}{JanusGraph} backends.}
        \resumeItem{\href{https://cv.jnapolitano.io/parts/data/data-integration/index.html}{CRM Application and Integration}}
          {Deployed a custom CRM solution with Microsoft SQL Server  in the Azure cloud.  \href{https://cv.jnapolitano.io/parts/data/data-integration/index.html}{Transformed data locally with Python to maximize value for clients.}}
      \resumeItemListEnd
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {\href{https://cv.jnapolitano.io/parts/resume/work-history/docs/ucf.html}{University of Central Florida}}{Orlando, FL}
      {Research Lead}{Jan 2017 - Aug 2019}
      \resumeItemListStart
        \resumeItem{\href{https://cv.jnapolitano.io/parts/analysis/political-analysis/terrorism-conflict/index.html}{Conflict Analysis}}
        {The Turkish-Kurdish Conflict is an ongoing armed struggle taking place in Anatolia.  The Turkish Government and armed groups terrorize each other and civilians.  Our work aims to detail the atrocities committed by any group or individual that maims or harms another.}
        \resumeItem{\href{https://cv.jnapolitano.io/parts/analysis/political-analysis/human-rights-law/index.html}{Human Rights Abuse Framework}}
          {A collection of Human Rights abuses as defined by international treaty used by research assistants to define crimes in conflict zones.}
        \resumeItem{\href{https://cv.jnapolitano.io/parts/analysis/political-analysis/terrorism-conflict/project-turkish-kurdish/pdf.htm}{Research Design}}
            {Created the procedures and manuals to train research assistants to query primary sources and code data points.}
        \resumeItem{\href{https://cv.jnapolitano.io/parts/analysis/political-analysis/terrorism-conflict/project-turkish-kurdish/database_schema.html}{Database Design}}
            {Defined a third normal database to maintain logical consistency.  Designed schema to facillitate data porting to a POLE graph database.}
        \resumeItem{\href{https://cv.jnapolitano.io/parts/data/data-integration/index.html}{Data Integration}}
            {Ensured integrity of data generated by research assistants.  Wrote python scripts to identify discrepancies in data coding. Integrated data from excel, json, and csv files.}
        \resumeItem{\href{https://cv.jnapolitano.io/parts/analysis/political-analysis/terrorism-conflict/project-turkish-kurdish/analysis.html}{Data Analysis}}
          {Analyzed conflict data with Pandas and Excel.  Prepared presenation that was peer reviewed at the Peace Science Conference at the Hague in Switzerland by Dr. Demet Mousseau.}
    \resumeItemListEnd

    \resumeSubheading
      {University of Central Florida}{Orlando, Fl}
      {Research Assistant}{Jan 2017 - Jan 2018}
      \resumeItemListStart
        \resumeItem{Data Integration}
          {Aggregated data points generated by student research assistants into database with Python.}
        \resumeItem{Sentiment Analysis}
          {Analyzed the sentiment of sentences to determine the emotional state of the speaker.}
        \resumeItem{Automated Sentiment Analysis}
          {Compared user scored sentences to sentiment scored by python scripts to identify human errors.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://cv.jnapolitano.io/parts/analysis/business-analysis/index.html}{Business Reporting and Sales Predictions}}
      {Reporting and Prediction completed for a retail chain of 57 stores.}
    \resumeSubItem{\href{https://cv.jnapolitano.io/parts/reference/build-this-site/index.html}{Sphinx CV Template}}
      {A sphinx project to enable non-programmers to create a static website of their cv with sphinx and MarkDown.}
    \resumeSubItem{\href{https://cv.jnapolitano.io/parts/data/graph-database/index.html}{Real Estate Professional Graph}}
      {Graph of real estate professionals in the United States.}
    \resumeSubItem{\href{https://cv.jnapolitano.io/parts/reference/configuration/index.html}{Development Setup Scripts}}
      {Scripts and instructions to  setup macs and other *nix systems for development.}
    \resumeSubItem{\href{https://cv.jnapolitano.io/parts/python-development/google/index.html}{Google Drive API}}
      {A google drive application to streamline data pipelines for teams using the google productivity suite.}
    \resumeSubItem{\href{https://cv.jnapolitano.io/parts/analysis/political-analysis/sup-court/project-sup-court-meta-data-graph/index.html}{Supreme Court Metadata Graph}}
      {A graph of the metadata of every United States Supreme Court Case.}
     \resumeSubItem{\href{https://cv.jnapolitano.io/parts/ml-ai/tensorflow/project-supcourt-tensorflow/index.html}{Supreme Court Voting Behavior Prediction in TensorFlow}}
      {Predicting voting behavior of Supreme Court justices with TensorFlow.}
     \resumeSubItem{\href{https://cv.jnapolitano.io/parts/ml-ai/tensorflow/project-gender-recognition/index.html}{Gender Recognition in TensorFlow}}
      {Identifying gender with TensorFlow.}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Langauages}
      {Bash, C, LaTeX, Python, SAS, SPSS, SQL.}
     \resumeSubItem{Technologies}
       {Azure, Docker, Git/GH, JanusGraph, Jupyter Notebook, Neo4j, Pandas, Shell, Sphinx, TensorFlow, Vim.}
%     \item{
%      \textbf{Languages}{: Bash, C, LaTeX, Python, SAS, SQL.}
%      \hfill
%      \textbf{Technologies}{: Azure, Docker, Git/GH, JanusGraph, Jupyter Notebook, Neo4j, Pandas, TensorFlow, Sphinx, Vim.}
%    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
