%-------------------------
% Resume in Latex
% Author : Justin Napolitano
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{parskip}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{0pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://jnapolitano.io/}{\Large Justin Napolitano}} & Email : \href{mailto:justin@jnapolitano,io}{justin@jnapolitano.io}\\
  \href{https://jnapolitano.io}{jnapolitano.io} & Mobile : +1-832-299-0372 \\
\end{tabular*}


%-----------------Letter-------------------------------
\section{}

\vspace{0.25in}

To whom it may concern, 

\vspace{0.15in}

\begin{flushleft}
    \begin{normalsize} 

        I currently work as an open source intelligence specialist identifying valuable sales leads with Networkx, JanusGraph and Neo4j graph databases.  I am proficient in Python, Pandas, MatPlotLib, SciPy, SAS, and SPSS analytic tools.  I am comfortable independently writing API requests and SQL queries to acquire data. I can also prepare reports and documents with tools such as LaTeX, Sphinx, and Jupyter Notebook. 

        I had worked with Dr. Demet Mousseau to record the history of human right abuses commmited in the Kurdish-Turkish conflict. \href{https://doi.org/10.1515/peps-2019-0036}{We developed the Turkish Kurdish Analysis Database that was presented at Peace Science Conference in 2019 and published in the journal Peace Economics, Peace Science and Public Policy.} My role required that I develop the research methodology, maintain a noSQL database, integrate data, and perform analysis.

        In August of 2019, I began treatment to successfully eliminate Leukemia from my bone marrow.  I could not work nor progress towards achieving a master's degree in international political economomy at the Korbel School, University of Denver at this time. I instead completed the Python specialization provided by the University of Michigan via Coursera. Supplementally, I trained in Pandas, MatPlotLib and Tensoflow on open source intelligence projects. 

        In May of 2021, I founded BTJN, LLC to complete contract work as a Python Developer.  My responsibilities include automating data pipelines, filtering data for valuable leads, and exporting data to external databases.   

        I would now like to work with the Central Intelligence Agency to identify threats to the United States and to prevent conflicts like those in Ukraine, Syria, and Yemen. I want to dedicate myself to ensuring that territories do not become conflict zones in order for civilians to live free of the atrocities of war.  I believe the role of the United States is to responsibly restrict the actions of uncooperative states and promote the common good of civilians within her sphere of influence. Please consider my request to aid in this mission.


        \vspace{.15in}

        Sincerely,

        \vspace{.15in}

        Justin Napolitano

    \end{normalsize}
\end{flushleft}

\end{document}

