%-------------------------
% Resume in Latex
% Author : Justin Napolitano
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://docs.jnapolitano.io/}{\Large Justin Napolitano}} & Email : \href{mailto:justin@jnapolitano,io}{justin@jnapolitano.io}\\
  \href{https://jnapolitano.io}{https:jnapolitano.io} & Mobile : +1-832-299-0372 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Central Florida}{Orlando, Fl}
      {Bachelor of Arts in Political Science}{August 2018}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://docs.jnapolitano.io/parts/data/web-scraping/index.html}{BTJN, LLC}}{Houston, TX}
      {Software Developer}{May 2021 - Present}
      \resumeItemListStart
        \resumeItem{\href{https://docs.jnapolitano.io/parts/data/web-scraping/index.html}{Sales Lead Generation Application}}
          {\href{https://docs.jnapolitano.io/parts/data/web-scraping/index.html}{Produced 10,000 sales leads weekly on average.  Mined web for data with Python and Bs4.} \href{https://docs.jnapolitano.io/parts/python-development/google/index.html}{Integrated data with custom Google API Class.}  Identified valuable leads with \href{https://docs.jnapolitano.io/parts/python-development/neo4j/index.html}{Neo4j} and \href{https://docs.jnapolitano.io/parts/python-development/janus-graph/index.html}{JanusGraph} backends.}
        \resumeItem{\href{https://docs.jnapolitano.io/parts/data/data-integration/index.html}{CRM Application and Integration}}
          {Deployed a custom CRM solution with Microsoft SQL Server in the Azure cloud.  \href{https://docs.jnapolitano.io/parts/data/data-integration/index.html}{Transformed data locally with Python to maximize value for clients.}}
        \resumeItem{\href{https://docs.jnapolitano.io/parts/analysis/business-analysis/index.html}{Business Reporting and Sales Predictions}}
          {Modeled retail sales with the SARINA, Holt-Winter, and Exponential Smoothing models in Python and Jupyter Notebooks.  Identified model of greatest predictive power with the Mean Absolute Percentage Error formula.}
      \resumeItemListEnd
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {\href{https://docs.jnapolitano.io/parts/resume/work-history/docs/ucf.html}{University of Central Florida}}{Orlando, FL}
      {Research Lead}{Jan 2017 - Aug 2019}
      \resumeItemListStart
        \resumeItem{\href{https://docs.jnapolitano.io/parts/analysis/political-analysis/terrorism-conflict/project-turkish-kurdish/pdf.htm}{Research Design}}
          {Ensured rigor of data collection methodology by meeting industry best practices.}
        \resumeItem{\href{https://docs.jnapolitano.io/parts/analysis/political-analysis/terrorism-conflict/project-turkish-kurdish/database_schema.html}{Database Design}}
          {Defined a third normal database to maintain logical consistency.  Refined schema to facilitate porting to Person, Object, Location and Events (POLE) schema.}
        \resumeItem{\href{https://docs.jnapolitano.io/parts/data/data-integration/index.html}{Data Integration}}
          {Standardized integration procedures to verify integrity of files generated by research assistants. Transformed data from Excel and CSV sources into JSON format to index into a noSQL database.}
        \resumeItem{\href{https://docs.jnapolitano.io/parts/analysis/political-analysis/terrorism-conflict/project-turkish-kurdish/analysis.html}{Data Analysis}}
          {Analyzed conflict data with Pandas and Excel.  Visualized data trends with MatPlotLib.  Prepared presentation for peer review at the Peace Science Conference at the Hague, Switzerland.}
        \resumeItem{\href{https://docs.jnapolitano.io/parts/analysis/political-analysis/terrorism-conflict/project-turkish-kurdish/pdf.html}{Project Management}}
          {Developed manuals to train inexperienced research assistants to query primary sources and code data points.  Led team to achieve project goals prior to deadlines defined in our research grant.}
        \resumeItem{\href{https://docs.jnapolitano.io/parts/analysis/political-analysis/human-rights-law/index.html}{Human Rights Abuse Frame Work}}
          {Aggregated corpus of international human rights law to cross reference with abuse events.}
    \resumeItemListEnd

    \resumeSubheading
      {University of Central Florida}{Orlando, Fl}
      {Research Assistant}{Jan 2017 - Jan 2018}
      \resumeItemListStart
        \resumeItem{Data Integration}
          {Aggregated data points generated by student research assistants into database with Python.}
        \resumeItem{Sentiment Analysis}
          {Analyzed sentiment of sentences to determine speaker's emotional state.}
        \resumeItem{Automated Sentiment Analysis}
          {Compared user scored sentences to programmatic scoring to identify errors.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://docs.jnapolitano.io/parts/analysis/business-analysis/index.html}{Business Analysis}}
      {Forecasting and analysis projects.}
    \resumeSubItem{\href{https://docs.jnapolitano.io/parts/analysis/political-analysis/index.html}{Political Analysis}}
      {Conflict, behavioral, and political analysis.}
    \resumeSubItem{\href{https://docs.jnapolitano.io/parts/ml-ai/index.htmll}{Machine Learning}}
      {Machine learning for political analysis.}
    \resumeSubItem{\href{https://docs.jnapolitano.io/parts/data/web-scraping/index.html}{Web Scraping}}
      {Web scraping projects to procure data.}
    \resumeSubItem{\href{https://docs.jnapolitano.io/parts/data/data-integration/index.html}{Data Integration}}
      {Data Integration and transformation scripts.}
    \resumeSubItem{\href{https://docs.jnapolitano.io/parts/python-development/google/index.html}{Google Drive API}}
      {Google API application to transform json data to Google Sheets.}
    \resumeSubItem{\href{https://journal.jnapolitano.io/parts/tutorials/sphinx/docs/build-this-site.html}{Sphinx Documentation Template}}
      {Tutorials and templates to create Sphinx and Jupyter Book publications}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Computer Languages}
      {Bash, C, LaTeX, Python, SAS, SPSS, SQL.}
    \resumeSubItem{Technologies}
      {Azure, Docker, Git, JanusGraph, Jupyter Notebook, Neo4j, Pandas, SciPY, Sphinx, TensorFlow.}
    \resumeSubItem{Data Modelling and Analysis}
      {\href{https://docs.jnapolitano.io/parts/analysis/business-analysis/project-retail-sales-forecasting/code-base/SalesForcasting.html}{Sales Forecasting,} {\href{https://docs.jnapolitano.io/parts/analysis/political-analysis/index.html}{Political Analysis,}} {\href{https://docs.jnapolitano.io/parts/analysis/business-analysis/index.html}{Business Analysis.}}}
    \resumeSubItem{Spoken Languages}
      {Cantonese, French, Spanish, Sranan Tongo.}
%     \item{
%      \textbf{Languages}{: Bash, C, LaTeX, Python, SAS, SQL.}
%      \hfill
%      \textbf{Technologies}{: Azure, Docker, Git/GH, JanusGraph, Jupyter Notebook, Neo4j, Pandas, TensorFlow, Sphinx, Vim.}
%    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
